\fontfamily{phv}\selectfont{Causal Discovery methods for Effective Connectivity in Human Brains}

### 2014-01-15 docs/paper/paper final.tex
Wrote first part of discussion.

\section{Discussion}
%Poor consistency between subjects
%Good consistency of structure within and between subjects
%inter-hemisphere connection
%cause of poor consistency: inherent to our method or viable for further research?
%data aquisition and noise, improvement in data -> improvement in causal inference
%better methods for direction (Tom's new algorithm), and why that might solve causal inference problems
%run-time is quick
%HRF

>>>>

\section{Discussion}
%Good consistency of structure within and between subjects
%cause of poor consistency: inherent to our method or viable for further research?
%data aquisition and noise, improvement in data -> improvement in causal inference
%better methods for direction (Tom's new algorithm), and why that might solve causal inference problems
%run-time is quick
%HRF

%Comparison with DWI inter-hemisphere connection
Standard PC and particularly the first, structural part, definitely has similarity with respect to existing methods based on DWI.
This is not completely surprising as standard PC yields a functional network and DWI based methods anatomical structural networks, two network types which are tightly related.
A less apparent observation is the clear presence of correlation between homologous area's in the functional network, which lacks in the structural network.
An explanation to this difference might be that these correlations respond to the long white-matter tracts connecting the two hemispheres through the corpus-callosum.
It is known that DWI has difficulty in measuring such long tracts, while the presence of correlation between two connected ends cannot be argued against.
As such, statistical baed causal discovery methods contribute additional information to finding structural connectivity.

% Comparison standard PC and EMS-PC
Both standard PC and EMS-PC find many bi-directional arrows, with some one-directional arrows.

%Poor consistency of directionality between subjects
There is some significant and consistent directionality within each of the subjects.
However the variance of this directionality between subjects is so high, there is no significant consistent one-directionality between them.
We were unable to find existing literature on connectivity methods regarding significant intra-subject one-directionality.

%Lack of symmetry
There is little to none symmetry in directionality between the two hemispheres within and across subjects.
One would at least expect some symmetry to be found.
This demonstrates that the gap between analytical methods for effective connectivity and anatomical correctness is still to wide.

% Further research
Further research may be done to investigating whether any of these arrows have a physiological meaning.
This can be done by repeating these experiment with more subjects to get a better view on the significance of the directional edges.

A Bayesian network cannot contain cycles, as that would imply that a variable is it's own ancestor and thus it's own cause.
However, exclusion of cycles in brain networks has not been proven and also seems unlikely.
We believe an interesting direction of further research would thus be to apply cyclical causal discovery.
% TODO: Add citation to Joris Mooij.

% TODO: What do you mean with 'it can also do this'? What does 'this' refer to?
% Computational advantage
%It can also do this quite efficiently, as a few hundred iterations can be run in a matter of hours per subject.
%We have not performed a statistical analysis on the number of iterations needed to stabilise the results.
%It may be possible that a significant result can already be found with much less iterations.

% TODO: Suggereren task based analysis ipv resting state voor beter causaal beeld. 
% TODO: Maak duidelijk welke aannames gedaan worden in welke PC variant en welke aannames verzwakt zouden kunnen worden.
